### 2011-11-03 Text/introduction.tex
Playing with velocity increase.

\section{Two unit cells results}
As far as one needs to restore the continuous picture one needs to make a simulation of a few
cells. This section provides results for two units. The results are summarized in Table
\ref{table:two_units}. The results for two sections are presented in Fig. \ref{fig:results:double}.
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_double_overall.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_double_first.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_double_second.eps}
\caption{Overall mass transfer coefficient (top left), first part (top
right), second part (bottom left).\label{fig:results:double}}
\end{figure}
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|}
$0.7392$&$1.0564$&$0.4220$\\
$1.8993$&$2.8301$&$0.9684$\\
$3.3925$&$4.7522$&$2.0328$\\
$3.7870$&$4.5615$&$3.0125$\\
\end{tabularx}
\caption{Simulation results for two units. \label{table:two_units}}
\end{table}

\section{Three unit cells results}
Three unit cells results are subdivided into three cells. We calculate the mass transfer
coefficients over the each cell, Fig. \ref{fig:results:triple}. The averaged coefficients  after
$3,300,000$ time steps are represented in Table. \ref{table:three_units}. The most important thing
is to look at the third column of the Table \ref{table:three_units} or for at the Fig. \ref{fig:re} 
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|X|}
0.4928&1.0564&2.8472e-05&0.4219\\
1.2662&2.8301&0.0146&0.9537\\
2.3110&4.7532&1.0665&1.1133
\end{tabularx}
\caption{Simulation results for three units.\label{table:three_units}}
\end{table}
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_overall.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_first.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_second.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_third.eps}\\
\caption{The mass transfer coefficient over time in different locations: overall mass transfer
coefficient (top left), first part (top right), second part (bottom left), third part (bottom
right). \label{fig:results:triple}}
\end{figure}

>>>>

\section{Two unit cells results}
As far as one needs to restore the continuous picture one needs to make a simulation of a few
cells. This section provides results for two units. The results are summarized in Table
\ref{table:two_units}. The results for two sections are presented in Fig. \ref{fig:results:double}.
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_double_overall.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_double_first.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_double_second.eps}
\caption{Overall mass transfer coefficient (top left), first part (top
right), second part (bottom left).\label{fig:results:double}}
\end{figure}
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
$0.7392$&$1.0564$&$0.4220$\\
$1.8993$&$2.8301$&$0.9684$\\
$3.3925$&$4.7522$&$2.0328$\\
$3.7870$&$4.5615$&$3.0125$\\
\hline
\end{tabularx}
\caption{Simulation results for two units. \label{table:two_units}}
\end{table}

\section{Three unit cells results}
Three unit cells results are subdivided into three cells. We calculate the mass transfer
coefficients over the each cell, Fig. \ref{fig:results:triple}. The averaged coefficients  after
$3,300,000$ time steps are represented in Table. \ref{table:three_units}. The most important thing
is to look at the third column of the Table \ref{table:three_units} or for at the Fig.
\ref{fig:results:triple} (bottom left). The coefficients for capillary numbers $0.026$ and $0.047$
are almost zero which indicates that the concentration at the first part of the channel is almost
the same as the second part. Thus, there is not enough time steps to transfer concentrate among
whole the channel (plug flow). In comparison with the first two values for capillary number $0.080$
the trend is different and concentrate is spread over the channel. However, the drop coefficients
are still inconsistents. Though last part and the second part exhibit close values (needed to tell
what is the real mass transfer coefficient). Overall, more time steps are needed.
$0.080$
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
0.4928&1.0564&2.8472e-05&0.4219\\
1.2662&2.8301&0.0146&0.9537\\
2.3110&4.7532&1.0665&1.1133\\
\hline
\end{tabularx}
\caption{Simulation results for three units.\label{table:three_units}}
\end{table}
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_overall.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_first.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_second.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_third.eps}\\
\caption{The mass transfer coefficient over time in different locations: overall mass transfer
coefficient (top left), first part (top right), second part (bottom left), third part (bottom
right). \label{fig:results:triple}}
\end{figure}

{\color{red} Probably we can consider that for capillary number less than $0.08$ the mass transfer
is a plug flow mass transfer, keeping only the impact from caps.}

\section{Four unit cells results}
Four unit cells results are subdivided into four cells. The results are presented in Fig.
\ref{fig:results:quadro}. While we expect certain deviations for the first and the last part, but
surprisingly the concentration difference over the third segment tends to be zero. That means not
enough time steps are performed. The results over segments are summarized in Table
\ref{table:four_units}.
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|}
\hline
$Ca$   &Overall  &I       &II      &III     &IV\\
$0.080$&$1.7359$ &$4.7533$&$1.0665$&$0.1088$&$1.0150$\\
$0.065$&$1.9260$ &$4.5620$&$0.9113$&$0.0619$&$2.1689$\\
\hline
\end{tabularx}
\caption{Simulation results for mass transfer coefficients for 4 unit cells
domain.\label{table:four_units}}
\end{table}
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_overall.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_first.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_second.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_third.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_quadro_fourth.eps}\\
\caption{The mass transfer coefficient over time in different locations: overall mass transfer
coefficient (top left), first part (top right), second part (middle left), third part (middle
right) and fourth part (bottom left). \label{fig:results:quadro}}
\end{figure}

From Figs. \ref{fig:results:triple} and \ref{fig:results:quadro} one can see that $4,000,000$ time
steps are enough to saturate the second unit for $Ca=0.080$ number. Let us recall bubble velocities
and see what are the characteristic lengths for them calculated as time steps multiplied on the
bubble velocity. From the table one can see that each unit cell is saturated with the timesteps as
$1.5 \frac{N_x}{U_{bubble}}$ {\color{red}(Pretty important result)}. It's inevitably needs the
velocity increase.
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}
\hline
$Ca$ &$U_{bubble}$ &$N_{iter_1}$ &$N_{iter_2}$ &$N_{iter_3}$ &$\frac{L_1}{N_x}$&$\frac{L_2}{N_x}$ 
&$\frac{L_3}{N_x}$\\
$0.026$&$0.0014$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$0.4666$ &$0.9333$ &$1.8666 $\\
$0.047$&$0.0027$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$0.9$    &$1.8$    &$3.6    $\\
$0.080$&$0.0045$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$1.5$    &$3.0$    &$6.0    $\\
$0.065$&$0.0037$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$1.2333$ &$2.4666$ &$4.9333 $\\
$0.222$&$0.0125$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$4.1666$ &$8.3333$ &$16.6666$\\
$0.479$&$0.0271$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$9.0333$ &$18.0666$&$36.1333$\\
$0.736$&$0.0416$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$13.8666$&$27.7333$&$55.4666$\\
$0.989$&$0.0559$&$10^6$&$2\cdot10^6$&$4\cdot10^6$&$18.6333$&$37.2666$&$74.5333$\\
\hline
\end{tabularx}
\caption{Table results to understand how many time steps are needed to be performed to reach the
saturation.\label{table:time:steps}}
\end{table}

\section{Improving velocity}

\section{Tweaking velocity}
This section does the job of increasing velocity results. The ulimate goal is to increase velocity
to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{\bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well. We make a few runs with velocities
$5,10,20,40$ times larger than original velocities.
